Check experimental design

### 2023-05-15 analysis/01_experimental-design.Rmd
Trying to build out aggregate interactions

# # Rename the variables
# colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
# 
# # Use dummy_cols() to get an index-coded version of all the attribute levels
# interactions <- dummy_cols(
#   interactions, 
#   select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
#   remove_first_dummy = FALSE,
#   remove_selected_columns = TRUE
# )
# 
# # Rename the index-coded variables
# colnames(interactions)[4:21] <- c(
#   str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
#   str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
# )
#
# org1 = amnesty
# org2 = greenpeace
# org3 = oxfam
# org4 = redcross
# gov_rel1 = friendly
# gov_rel2 = criticized
# gov_rel3 = crackdown

# Build out all the necessary interactions...
# ...by multiplying together the needed index-coded levels.
interactions <- interactions %>% 
  as_tibble() %>% 
  mutate(
    h2b_1 = ifelse(Organization ==3|Organization==4, 1, 0), # 1 if org is oxfam or redcross
    h2b_2 = ifelse(`Relationship with host government` == 2|`Relationship with host government` == 3, 1, 0), # 1 if gov_rel is criticized or crackdown
    h2b_3 = h2b_1*h2b_2 # interaction term
    )

>>>>

# # org1 = amnesty
# # org2 = greenpeace
# # org3 = oxfam
# # org4 = redcross
# # gov_rel1 = friendly
# # gov_rel2 = criticized
# # gov_rel3 = crackdown
# 
# # Build out all the necessary interactions...
# # ...by multiplying together the needed index-coded levels.
# interactions <- interactions %>% 
#   as_tibble() %>% 
#   mutate(
#     h2b_1 = ifelse(Organization ==3|Organization==4, 1, 0), # 1 if org is oxfam or redcross
#     h2b_2 = ifelse(`Relationship with host government` == 2|`Relationship with host government` == 3, 1, 0), # 1 if gov_rel is criticized or crackdown
#     h2b_3 = h2b_1*h2b_2 # interaction term
#     )

interactions <- interactions |> 
  mutate(
    # Oxfam or Red Cross.
    h2b_org_1 = ifelse(org3 == 1 | org4 == 1, 1, 0),
    # Government crackdown or criticism.
    h2b_gov_rel_1 = ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
    # Oxfam or Red Cross facing government crackdown or criticism.
    h2b_int_1 = ifelse(org3 == 1 | org4 == 1, 1, 0) * ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
    # Amnesty or Greenpeace.
    h2b_org_2 = ifelse(org1 == 1 | org2 == 1, 1, 0),
    # Government crackdown.
    h2b_gov_rel_2 = gov_rel3,
    # Amnesty or Greenpeace is facing crackdown.
    # h2b_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
    h2b_int_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
  )
  # select(1:3, contains("h2b"))

# interactions |> 
#   # select(org1:org4, gov_rel2:gov_rel3, h2b_1, h2b_2)
#   # select(org3, org4, gov_rel2, gov_rel3, h2b_1)
#   select(org1, org2, gov_rel3, h2b_2)
